---
title: "Title"
subtitle: "<br><br> Introduction to Data Science"
author: "[introds.org](https://introds.org/)"
date: "<br> Dr. Mine Çetinkaya-Rundel"
output:
  xaringan::moon_reader:
    css: ["../../xaringan-themer.css", "../../slides.css"]
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightLines: true
      highlightStyle: solarized-light
      countIncrementalSlides: false
---

```{r child = "../../setup.Rmd"}
```

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(emo)
```

class: middle

# Section title

---

class: inverse

## Inverse `class: inverse`

Use for full page figures

---

## Sample slide

- with
- tight
- bullet
- points

---

## Sample slide

- with

- spaced out

- bullet

- points

---

# Colored text

- .dark-blue[dark-blue] $\leftarrow$ there's also dark-blue
- .light-blue[light-blue]
- .green[green]
- .gray[gray]
- .pink[pink]
- .yellow[yellow]

---

## Text alignment

left

.right[right]

.center[center]

---

## Font sizes

- .huge[huge = 400%]
- .larger[larger = 250%]
- .large[large = 125%]
- .midi[midi = 85%] 
- .small[small = 70%]
- .xsmall[xsmall = 60%]
- .tiny[tiny = 50%]

---

## Huge numbers

.pull-left[
  huge-blue-number  
  .huge-blue-number[1]
]
.pull-right[
  huge-pink-number    
  .huge-pink-number[2]
]

---

## Handwriting

- text
- .hand[hand]
- .hand[.pink[hand with]]
- .hand[.green[other colors]]

---

## Two columns, equal width

.pull-left[
- text 
- on
- left
]
.pull-right[
```{r}
2 + 1
plot(cars) #<<
```
]

---

## Two columns, wider left

.pull-left-wide[
- text 
- on
- left
]
.pull-right-narrow[
```{r}
2 + 1
plot(cars) #<<
```
]

---

## Two columns, wider right

.pull-left-narrow[
- text 
- on
- left
]
.pull-right-wide[
```{r}
2 + 1
plot(cars) #<<
```
]

---

## Footnote

Some text<sup>+</sup>

.footnote[<sup>+</sup>Footnote]

---

## Custom boxes

.question[
A question: What is data science?
]

.your-turn[
Some instructions: Figure out what data science is...
]

.tip[
A tip: Nobody knows what data science is!
]

---

## ggplot

```{r out.width="55%"}
library(ggplot2)
ggplot(mpg, aes(x = hwy, y = cty, color = drv)) +
  geom_point() #<<
```

---

## tibble

```{r}
mpg
```

---

## kable

```{r}
library(knitr)
kable(mpg)
```

---

```{r}
library(DT)
datatable(mpg)
```

